|

### 2023-10-24 paper/paper.qmd
Increase big.interval for writing numbers
Add keywords

---
title: |
        '*Zijt* gij dat of *bent* gij dat?'
subtitle: Een alternantiestudie van de tweede persoon enkelvoud van *zijn* in Vlaamse tussentaal
abstract: |
  In Colloquial Belgian Dutch (CBD) *gij bent*, a special form of the second person singular of *zijn* ('to be'), has appeared, which blends the historically traditional form *gij zijt* with Standard Dutch *bent* from *jij bent*. A logistic regression analysis and general additive model of CBD tweets show that *gij bent* is popular only in the Brabant dialect area and that usage is highest in the northern Antwerp area. *Gij bent* is also more likely to appear in tweets with general statements rather than conversations, which hints at a formality difference. Tweets thought to come from women also feature more *gij bent*. It is plausible that *gij bent* was able to spread throughout the Brabant dialect area because of a formality reinterpretation. While the form likely originates from the northern Antwerp dialects, it might have been reinterpreted as an innovative, hybrid form in CBD, but only in the Brabant area.
abstract-title: Abstract
author:
  - name: Anthe Sevenants
    email: anthe.sevenants@kuleuven.be
    orcid: 0000-0002-5055-770X
    affiliations:
      - name: KU Leuven
format: 
   html:
      df-print: kable
   docx:
      df-print: kable
      toc: false
include-in-header:
  - text: |
      <style>
      h1 {
        text-align: center;
      }
      </style>
crossref:
  sec-prefix: "Sectie"
editor: visual
css: paper.css
title-block-banner: true
bibliography: references.bib
toc: true
toc-depth: 4
toc-location: left
tbl-cap-location: bottom
fig-cap-location: bottom
number-sections: true
reference-location: margin
csl: chicago-author-date.csl
execute:
  echo: false
lang: nl
---

@@

formatn <- function(number) {
    format(round(as.numeric(number), 1), nsmall=0, big.mark=".")
}

>>>>

---
title: |
        '*Zijt* gij dat of *bent* gij dat?'
subtitle: Een alternantiestudie van de tweede persoon enkelvoud van *zijn* in Vlaamse tussentaal
abstract: |
  In Colloquial Belgian Dutch (CBD) *gij bent*, a special form of the second person singular of *zijn* ('to be'), has appeared, which blends the historically traditional form *gij zijt* with Standard Dutch *bent* from *jij bent*. A logistic regression analysis and general additive model of CBD tweets show that *gij bent* is popular only in the Brabant dialect area and that usage is highest in the northern Antwerp area. *Gij bent* is also more likely to appear in tweets with general statements rather than conversations, which hints at a formality difference. Tweets thought to come from women also feature more *gij bent*. It is plausible that *gij bent* was able to spread throughout the Brabant dialect area because of a formality reinterpretation. While the form likely originates from the northern Antwerp dialects, it might have been reinterpreted as an innovative, hybrid form in CBD, but only in the Brabant area.
abstract-title: Abstract
author:
  - name: Anthe Sevenants
    email: anthe.sevenants@kuleuven.be
    orcid: 0000-0002-5055-770X
    affiliations:
      - name: KU Leuven
keywords:
  - Dutch
  - Flemish
  - corpus linguistics
  - tussentaal
  - Standard Language
  - diaglossia
format: 
   html:
      df-print: kable
   docx:
      df-print: kable
      toc: false
include-in-header:
  - text: |
      <style>
      h1 {
        text-align: center;
      }
      </style>
crossref:
  sec-prefix: "Sectie"
editor: visual
css: paper.css
title-block-banner: true
bibliography: references.bib
toc: true
toc-depth: 4
toc-location: left
tbl-cap-location: bottom
fig-cap-location: bottom
number-sections: true
reference-location: margin
csl: chicago-author-date.csl
execute:
  echo: false
lang: nl
---

@@

formatn <- function(number) {
    format(round(as.numeric(number), 1), nsmall=0, big.mark=".", big.interval=4L)
}
